03 Data Vizualization

### 2022-05-13 03_data_viz.Rmd
added weighted dF with mem effect

```{r lit analysis data}
lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
turnover_means <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>%
  select(terrain, u_d_weighted) %>% 
  rename(u_d_mn = u_d_weighted) %>% 
  mutate(comment = terrain) %>% 
  mutate(n = case_when(
    terrain == "Niwot Ridge Tundra" ~ 3,
    terrain == "Gordon Gulch Conifer Forest" ~ 1,
    terrain == "Marshall Mesa Grassland" ~ 2
  )) %>% 
  mutate(method = "LH-SIP",
         method_type = "LH-SIP")

@@

```{r cowplot mooooo}
p_community_turnover_cow <- cowplot::plot_grid(
  p_turnover_distributions,
  p_gen_time_mean,
  labels = "AUTO",
  rel_widths = c(1,1),
  align = "h",
  nrow = 1
)

# 
# save_plot(filename = "fig_output/p_community_turnover_cow.png",
#           plot = p_community_turnover_cow,
#           base_height = 5,
#           base_width = 10
#           )

@@

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF
    )
  ) +
  # Weighted data here:
  geom_line(aes(
    x = inc_time_d,
    y = dF_weighted,
    color = terrain),
    size = 1.5,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      x = inc_time_d,
      y = dF_weighted,
      color = terrain,
      fill = terrain),
    size = 2,
    alpha = 0.5
    ) +
  # Unweighted data here:
  geom_borderline(
    data = turnover_summarized,
    aes(group = compound),
    color = "gray"
) +
  geom_point(
    data = turnover_summarized,
    size = 2,
    alpha = 0.5
    ) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(
    xlim = c(0, 8),
    clip = "off"
    ) +
  facet_wrap(vars(terrain),
             nrow = 1) +
  labs(x = "Incubation Time (Days)",
       y = TeX("$ \\Delta ^2H$ (at%)"),
       ) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))

@@

peaks_mapped_summarized_wppm <- turnover_summarized %>% 
    mutate(at2H_ppm = at2H * 10000,
         at2H_mn_zero_ppm = at2H_mn_zero * 10000,
         at2H_weighted_ppm = at2H_weighted * 10000)

>>>>

```{r lit analysis data}
lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))

turnover_means <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>%
  select(terrain, u_d_weighted) %>% 
  rename(u_d_mn = u_d_weighted) %>% 
  mutate(comment = terrain) %>% 
  mutate(n = case_when(
    terrain == "Niwot Ridge Tundra" ~ 3,
    terrain == "Gordon Gulch Conifer Forest" ~ 1,
    terrain == "Marshall Mesa Grassland" ~ 2
  )) %>% 
  mutate(method = "LH-SIP",
         method_type = "LH-SIP")

@@

@@

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>% view()

  ggplot(
    aes(
      x = inc_time_d,
      y = dF
    )
  ) +
  # Weighted data here:
  geom_line(aes(
    x = inc_time_d,
    y = dF,
    color = terrain),
    size = 1.5,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      x = inc_time_d,
      y = dF,
      color = terrain,
      fill = terrain),
    size = 2,
    alpha = 0.5
    ) +
  # Unweighted data here:
  geom_borderline(
    data = turnover_summarized,
    aes(group = compound),
    color = "gray"
) +
  geom_point(
    data = turnover_summarized,
    size = 2,
    alpha = 0.5
    ) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(
    xlim = c(0, 8),
    clip = "off"
    ) +
  facet_wrap(vars(terrain),
             nrow = 1) +
  labs(x = "Incubation Time (Days)",
       y = TeX("$ \\Delta ^2H$ (at%)"),
       ) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))

@@

peaks_mapped_summarized_wppm <- turnover_summarized %>% 
    mutate(
      at2H_ppm = calibrated_at2H_without_memory * 10000,
      at2H_ppm_mc = calibrated_at2H_with_memory_correction * 10000,
      at2H_mn_zero_ppm = at2H_mn_zero * 10000,
      at2H_weighted_ppm = at2H_weighted * 10000)
